\documentclass{article}
\usepackage{tabularx,hyperref,booktabs}
\usepackage[margin=1in]{geometry}

\begin{document}
  \begin{description}
\item[Make--Up Policy:] Make--up exams are not likely and are to not be expected. Whether or not an exam can be made up is at the discretion of the instructor.

\item[Extra Credit:] Extra credit may be given at the discretion of the instructor, and will \textbf{not} be given on an individual basis.

\item[Additional expectations:]
  Students are expected to regularly communicate any issues or concerns with their instructor. Since provisions already exist in the syllabus to reward extraordinary effort, special requests regarding final grades will \textbf{not} be acknowledged.

  If you are worried about your grade or you are struggling in the course, you should contact me immediately (e.g. during finals week is generally considered ``too little, too late'').

\item[Classroom Responsibilities: (Approved by the Lander Faculty)]\ \newline
  All Lander students will \dots
  \begin{itemize}
    \item read and follow their professors' syllabi, including course guidelines and procedures, to be prepared for class
    \item check their Lander email accounts daily and check blackboard daily (if used in class) for class announcements, assignments, etc.
    \item be aware of each professor’s absence and tardy policies
    \item communicate concerns about classes to their professors, including asking for clarification if the student does not understand an assignment or expectations
    \item be courteous to peers, professors, and the learning environment, avoiding the following disruptive classroom behaviors: sleeping, inappropriate talking, inappropriate laptop use, rudeness, doing homework for other classes, text messaging, or answering cell phones
    \item not give, use, or receive unauthorized aid in academic activities because these are serious violations of academic integrity
    \item know and accept the consequences of committing plagiarism, which could include receiving a failing assignment grade, failing the course, or being suspended from the University.
  \end{itemize}

\item[Reference to Lander’s Honor Code:]
  The Lander University Academic Honor Code may be found in the Lander Student Handbook. You are responsible for understanding the possible consequences of violating the code.

\item[Reference to Lander’s inclement weather policy:]
  I encourage you not to risk traveling to campus if weather conditions are hazardous and prevent safe travel. If you miss a class due to travel conditions and the University is not closed you are responsible for all material covered in class during your absence. Whenever classes are canceled, Lander will inform local TV and radio stations. In addition information will be posted at the Lander website: \href{www.lander.edu}{www.lander.edu}. A recorded message will also be provided at (864) 388-8000.

\item[Reference to Lander’s ADA policy:]
  Lander University recognizes its responsibility for creating an
  institutional climate where students with disabilities can
  thrive. If you have any type of disability that requires
  accommodations, please contact the Student Success Center at
  \href{mailto:accessibilityservices@lander.edu}{accessibilityservices\allowbreak@lander.edu}
  or (864) 388-8308 to discuss your needs. Once the Student Success
  Center has received appropriate documentation, your instructors
  will be informed of approved accommodations.

  \textbf{If you are approved for test accomodations, please email me at
  least 48 hours in advance of the exam so that I may make arrangements!}

\item[Use of Electronic Devices Policy:]
  Instructors will notify students when the use of particular devices is appropriate or inappropriate during class. If an extenuating circumstance requires students to use their device for a non-pedagogical purpose during class, the instructor should be notified as soon as possible.

  If you are using any distracting electronic devices (phones, watches, computers, etc.), you will be asked to leave class immediately and marked as absent.

  If you need to take a text or call quietly step out of class to engage.

\item[AI Policy:]
  Lander University recognizes the impact that emerging technologies such as generative artificial intelligence (AI) have on higher education, including both their usefulness as intellectual and creative tools and their potential to be used as vectors of academic dishonesty. In this class it is not permitted to use any AI without prior approval from the instructor.
    %TODO

\item[Notice of Nondiscrimination:]

  Lander University is committed to a policy of equal opportunity for all persons and does not discriminate on the basis of race, color, religion, sex, sexual orientation, gender, gender identity, gender expression, pregnancy, childbirth or related medical conditions, national origin, age, disability, veteran’s status, genetic information or protected activity (e.g., opposition to prohibited discrimination or participation in any complaint process, etc.) in employment, educational programs and activities, admissions and financial aid. This includes a prohibition against sexual harassment and sexual violence as mandated by Title IX of the Education Amendments of 1972.

  Individuals experiencing sex-based discrimination, sexual harassment, or sexual violence are encouraged to contact the Title IX Coordinator in person, mail, telephone, electronic mail, using the contact information listed for the Title IX Coordinator, or by completing an online complaint form. Reports may be made at any time (including during non-business hours) by using the telephone number or electronic mail address, or by mail to the office address.

\begin{quote}
  \begin{tabular}{@{}ll@{}}
    Title IX Coordinator: & Jalysa Green\\
    Office Phone: & (864) 388-8905\\
    Office Location: & Room 349, Grier Student Center\\
    Mailing Address: & 320 Stanley Avenue, CPO Box 6012, Greenwood, SC 29649
  \end{tabular}
\end{quote}

  Please visit \href{https://www.lander.edu/about/offices-departments/title-ix/index.html}{lander.edu/about/offices-departments/title-ix/index.html} and \href{https://www.lander.edu/about/statement-non-discrimination}{lander.edu/about/\allowbreak statement\allowbreak -non\allowbreak -discrimination} to review the applicable policies, access the complaint forms, and learn more about the pertinent grievance processes

\item[Changes to Syllabus and/or calendar:]
  The instructor reserves the right to change this syllabus and/or calendar when necessary for clarity or typos, to meet learning objectives, and to compensate for missed classes. All changes to these documents will be announced in class, by e-mail, or through Blackboard.

  \end{description}
\end{document}